%%
% BIThesis 本科毕业设计论文模板 —— 使用 XeLaTeX 编译 The BIThesis Template for Undergraduate Thesis
% This file has no copyright assigned and is placed in the Public Domain.
%%

% 中英文摘要章节
\begin{abstract}
面向非结构化桌面的物体抓取与放置是服务机器人与智能产线的常见需求，视觉—语言—动作模型能够融合多相机视觉、自然语言指令与本体状态，
为复杂操作提供统一的策略表示。然而从开源算法到具体实验室硬件，仍需在实时控制、数据规范与实机部署之间建立可复现闭环。
本文以 Franka 七自由度机械臂与二指夹爪为平台，在 Hugging Face LeRobot 框架下扩展通用机器人与遥操作接口：实时侧采用基于官方库与轨迹平滑的服务进程，
上位机通过套接字与其解耦；实现 Franka 从机机器人抽象及三维鼠标笛卡尔增量遥操作、同构主从关节空间示教，并给出两阶段配对标定流程，
将关节缩放偏置与夹爪量程写入可版本化配置，以提高示教轨迹的可重复性。在此基础上采集桌面苹果抓取任务示教数据，按
 LeRobot 数据集规范组织多路 RGB 与八维关节—夹爪状态及动作，得到小规模专用数据集。算法侧选取 $\pi_{0.5}$ 型视觉—语言—动作模型，
 在加载预训练权重的前提下完成观测与动作空间向 OpenPI 训练接口的映射与任务微调。实机实验表明，在相同网络权重下，采用分段同步闭环、
 短窗口执行动作块并高频重推理的部署方式，抓取成功率由约百分之五提升至接近百分之百；验证了闭环执行策略对接触敏感任务的决定性作用。
 全文形成了从底层接入、示教采集、模型训练到在线控制的完整技术路线，可为同类平台落地提供工程参考。
\end{abstract}

% 如需手动控制换行连字符位置，可写 aa\-bb，详见
% https://bithesis.bitnp.net/faq/hyphen.html

% 英文摘要章节
\begin{abstractEn}
Unstructured desktop pick-and-place remains a recurring need in service robotics and intelligent automation. Vision-language-action (VLA) models unify multicamera perception, natural-language task prompts, and proprioceptive state, offering a single policy representation for complex manipulation. Bridging open-source learning stacks to laboratory hardware nonetheless requires a reproducible path through real-time control, dataset conventions, and deployable closed-loop execution. This thesis targets a Franka seven-degree-of-freedom arm with a parallel gripper. Within the Hugging Face LeRobot ecosystem, we implement follower abstractions and teleoperation extensions: a real-time service built on the vendor library with trajectory smoothing talks to the training machine over sockets; we add SpaceMouse Cartesian teleoperation and homomorphic leader--follower joint-space teaching, together with a two-stage pairing calibration that writes per-joint scales and offsets and gripper endpoints to versioned configs, improving demonstration repeatability. Demonstrations for a desktop apple-grasp task are recorded into a LeRobot~v2.1-compliant multimodal dataset with dual RGB streams and eight-dimensional joint--gripper state and actions at modest scale. On the algorithm side, we map observations and actions to the OpenPI training interface and fine-tune a $\pi_{0.5}$ VLA from pretrained weights. On hardware, the same checkpoint under asynchronous chunk execution achieves only about $5\%$ success, whereas a segmented synchronous closed-loop policy that executes a short slice of each predicted action chunk before re-inferring raises success to nearly $100\%$, showing that online closing of the loop dominates performance on contact-rich grasps. The work delivers an end-to-end pipeline from integration and data collection through training and real-time control, as a reference for similar platform bring-up.
\end{abstractEn}
